### 2015-08-08 ThesisJo/derivations.tex
la2pdf commit - 2015:08:08	15:03:27	(Sat 8.Aug)
la2pdf commit - 2015:08:08	15:34:50	(Sat 8.Aug)

@@

>>>>

\begin{align}
\text{Coherent Gain} &= W(0) = \sumb{m}{}w_m
\end{align}

\begin{align}
\text{Coherent Power Gain} &= \big|W(0)\big|^2 = \big|\sumb{m}{}w_m \big|^2
\end{align}

\begin{align}
\text{Incoherent Power Gain} &= \sumb{m}{}w_m^2
\end{align}

\begin{align}
\text{Equivalent Noise Bandwidth} &= \big|W(0)\big|^2 = \big|\sumb{m}{}w_m \big|^2
\end{align}

\begin{align}
\text{Equivalent Noise Bandwidth} &= \frac{\text{Coherent Power Gain}}{\text{Equivalent Noise Bandwidth}} = \frac{\big|\sumb{m}{}w_m \big|^2}{\big|\sumb{m}{}w_m \big|^2}
\end{align}

Scallopping loss:
\begin{align}
\text{SL} &= \frac{\left|W\left(\frac{\pi}{2OMd}\right)\right|}{W(0)} = \frac{\left|\sumb{m}{}w_m\;e^{-j\k\cdot\p_m}\right|}{\sumb{m}{}w_m}
\end{align}

@@

Narrow ones:
- Best coherent gain, lowest equivalent noise bandwidth, and most sensitive to steering meaning not needing to steer as much for some effect.
